---
title: "Cabbages"
author: "Diego Martinez"
date: "5/31/22"
output:
  html_document:
    df_print: paged
--- 

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$:There is no difference between the Vitamin content based on the cultivation methods of c39 and c52.   

$H_A$:There is a difference between the Vitamin c content based on the cultivation methods of c39 and c52.   

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

We are explaining a vitamin c numerical variable by examining the categorical variable cultivation. We are using a T test to compare the vitamin content in both groups.     

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(VitC~Cult,data=veggy)
```

The mean for c39 is a few numbers above 50. The mean for c52 is in between 60 & 70 (close to 75). c39 had an overall lower mean for the amounts of vitamin C. c52 has a much higher mean. This could be due to random chance, we still aren't sure. 

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The cultivation method c39 had a median of 51.0. While c52 had a median of 64.5. c39 had a mean of 51.5 and c52 had a mean of 64.4. c52's minimum is 6 higher than c39's. This means that the cultivation method c52 was more successful in producing Vitamin C. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
